---
title: "iteration_class"
author:  "Alexey Abramov"
date: "11/9/2020"
output: 
  github_document:
    toc: true
---

# Setup

```{r, setup}
library(tidyverse)
library(readr)
library(rvest)


knitr::opts_chunk$set(
  fig.width = 6,
  fig.height = 6,
  out.width = "90%"
)

theme_set(
  ggthemes::theme_fivethirtyeight() + theme(legend.position = "bottom")
  )

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.colour = "viridis"
)

scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

Load in dataset
```{r}
homicide_df = read_csv("data/homicides.csv")
```

Data wrangling
```{r}
homicide_df =
  homicide_df  %>% 
  mutate(
    city_state = str_c(city, state, sep = "_"),
    resolved = case_when(
            disposition == "Closed without arrest" ~ "unsolved",
            disposition == "Open/No arrest" ~ "unsolved",
            disposition == "Closed by arrest" ~ "solved")) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL")
```

```{r}
aggregate_df =
  homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved =="unsolved")
  )
```

Can I do a prop test for a single city?
```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved),
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)) %>% 
  broom::tidy()
```

```{r}
results_df =
  aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x = prop_tests, ~ broom::tidy(.x))) %>% 
  select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high)
```

Graphing results
```{r}
results_df %>% 
  mutate(
    city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() + 
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high))
```

# Problem 2 ideas...

Import one data set

data_1 = read_csv lda_data / con_01.csv
list.files("lda_data")...
Put that into a tibble ... 

path_df = tibble(
  path = list.files("lda_data")) %>% 
  mutate(path = str_c("lda_data/", path),
  data = map(........)
  
Control vs. Experiment...
  Mutate, str_c, pivot_longer for the dates

path_df$path[[1]]
read_csv(path_df$path[[1]])

```{r}
```


